---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  echo     = FALSE,
  message  = FALSE,
  warning  = FALSE
)

library(webshot2)
library(tidyRSS)
library(glue)
library(stringr)
library(dplyr)
library(purrr)
```

### Hi, I'm Jared ðŸ‘‹

I'm a Senior Bioinformatics Research Scientist in Suzanne Baker's lab in the Department of Developmental Neurobiology at St. Jude Children's Research Hospital.
We study oncohistone mutations in the context of pediatric high grade gliomas.

Other than analysis, I build useful tools and utilities for the lab and community. 
Recently, I created a basic utility called [**strprofiler**](https://github.com/j-andrews7/strprofiler) for comparing STR profiles between large collections and identifying potential sample swaps.
This is particularly useful for labs that generate many cell lines/models, as we do.

Lately, I've been working on an R package called [**CRISPRball**](https://github.com/j-andrews7/CRISPRball), which is largely based around a Shiny app of the same name for exploring, visualizing, and comparing CRISPR-Cas9 screens analyzed with [**MAGeCK**](https://sourceforge.net/projects/mageck/).
While this is a work in progress, it is functionally complete and will hopefully be in the next release of Bioconductor.

I am/have been involved in a handful of Bioconductor packages, including [dittoSeq](https://bioconductor.org/packages/release/bioc/html/dittoSeq.html), [SingleR](https://bioconductor.org/packages/release/bioc/html/SingleR.html), [escape](https://bioconductor.org/packages/release/bioc/html/escape.html), and [celldex](http://bioconductor.org/packages/release/data/experiment/html/celldex.html).

### Here's some stats on my GitHub repos

<p align="center">
    <img src="https://github-readme-stats.vercel.app/api?username=j-andrews7&show_icons=true&theme=dracula">
    <img src="https://github-readme-stats.vercel.app/api/top-langs/?username=j-andrews7&hide=html,css,jupyter%20notebook&layout=compact">
</p>


### My recent GitHub activity

```{r github, results = "asis"}
activity <- tidyfeed("https://github.com/j-andrews7.atom") %>%
    arrange(desc(entry_last_updated)) %>%
    slice_head(n = 10)

map_chr(activity$entry_title, function(.title) {
    title <- str_remove(.title, "^j-andrews7 ")
    title_split <- str_split(str_to_sentence(title), " ", simplify = TRUE)
    repo <- title_split[length(title_split)]
    repo_link <- glue("[{repo}](https://github.com/{repo})")
    event_type <- title_split[1]
    event <- glue_collapse(title_split[-length(title_split)], sep = " ")
    emoji <- case_when(
        event_type == "Commented" ~ "ðŸ—£",
        event_type == "Closed"    ~ "ðŸŽŠ",
        event_type == "Merged"    ~ "ðŸŽ‰",
        event_type == "Opened"    ~ "ðŸ¤”",
        event_type == "Pushed"    ~ "ðŸ“¨",
        event_type == "Starred"   ~ "â­ï¸",
        event_type == "Forked"    ~ "ðŸ´",
        event_type == "Released"  ~ "ðŸ“¦",
        TRUE                      ~ "ðŸ˜º"
    )
    glue("* {emoji} {event} {repo_link}")
})  %>%
    paste(collapse = "\n") %>%
    cat()
```

